Classifier Construction

### 2019-03-29 Code/dallin_annotations/08_classifier_construction.Rmd
Updated the documents in dallin_annotations.

```{r}
library(tidyverse)
library(fastrtext)
library(magrittr) # for assignment operator %<>% 
library(plotly)
require(randomForest)
library(Matrix)
source("R/clus_func.R")
source("R/logit_classifier_func.R")

@@

set.seed(123)

# Fasttext train ----------------------------------------------------------

# train unsupervised fasttext model to learn tweet semantics and word vector representations

# file to read tweets from. Should be a txt file with one tweet per line
file_txt <- "data/tweet_sample_2M_noRT.txt"

# new file to write the trained model to
file_model50  <- "models/fullClassifierOne/model50-tweet_sample_2M_noRT.dat"

@@

# load the model object we just trained
fasttext_model <- load_model(file_model50)

# Fasttext model evaluation -----------------------------------------------

>>>>

# Libraries
```{r}
library(tidyverse)
library(fastrtext)
library(magrittr) # for assignment operator %<>% 
library(plotly)
require(randomForest)
library(Matrix)
source("R/clus_func.R")
source("R/logit_classifier_func.R")

@@

set.seed(123)
```

##### Look at working directory
```{r}
getwd()
```

# Train and Load the fastText Model
Unsupervised fastText models produce word vectors. In other words, the create a mathmatical representation of the word. 
```{r}
# Fasttext train ----------------------------------------------------------
# train unsupervised fasttext model to learn tweet semantics and word vector representations

# file to read tweets from. Should be a txt file with one tweet per line
file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"

# new file to write the trained model to
file_model50  <- "../../Temporary/model50-tweet_sample_2M_noRT.dat"

@@

# load the model object we just trained
fasttext_model <- load_model(file_model50)
```

```{r}
# Fasttext model evaluation -----------------------------------------------
